---
title: "Lab 00 - Hello IDS!"
author: "Tay Nash"
date: "`r Sys.Date()`"
output: html_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
```

### Exercises 16-17

We set up the data frame. Edit the data below to include information about your team members.

```{r setup-tibble}
team_data <- tibble(
  name = c("Tay Nash", "member 1", "member 2", 
           "member 3", "member 4"),
  github_username = c("taynash", "username 1", "username 2", 
                      "username 3", "username 4"), 
  colour = c("darkgreen", "colour 1", "colour 2", 
             "colour 3", "colour 4"),
  hobby = c("gym", "hobby 1", "hobby 2", 
            "hobby 3", "hobby 4"),
  favourite_number = c(4, NA, NA, NA, NA)
  )

team_data
```

### Exercise 18

We now work on visualising our data. 

```{r bar-plot}
p1 <- ggplot(data = team_data, 
             mapping = aes(x = github_username, 
                           y = favourite_number,
                           fill = colour), 
             ) +
   geom_col() +
   scale_fill_identity()
p1
```


This graph shows the groups info with Github Username on the x-axis and their favourite number on the y-axis. The colour of the bar represents their favourite colour.

### Exercises 19

Change the text of the plot title and axis labels.

```{r labelled-bar-plot}
p1 + labs(x = "Github Username", 
          y = "Favourite Number",
          title = "Group Info")
```

### Exercise 20

```{r new-bar-plot}
p2 <- ggplot(team_data, aes(x = hobby)) +
  geom_bar()
p2
```

Hobbies vary person to person and it is unlikely that people have the same hobby, so if we were to increase the dataset to include more people on the course, whilst there may be repeated results the number of possible answers will still be similar to the number of entities therefore the data would still not be suitable.

